---
title: "MA615_HW_1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load tidyverse, using the library() command so that you can use all the required functions such as ggplot. Load your data into R using the data() command.

```{r setup, include=FALSE}
library(tidyverse)

# call built-in data mtcars.
data(mtcars)
```

Select car models where mpg is less than 20 by creating another column and assigning them to a new data set.

```{r setup, include=FALSE}

# Select only car models where mpg<20
mtcars_mpg2 <- mtcars[mtcars$mpg < 20,]
```

In this new data set, reduce the variables in your data and leave only the relevant ones 

```{r setup, include=FALSE}
# Reduce the variables to mpg, cyl, disp, hp, gears
mtcars_mpg2 <- mtcars_mpg2[, c(1,2,3,4,10)]
```

Read the handfunctions.R file so you can use it to 
```{r setup, include=FALSE}
# read the R file hand_functions.R so that it can be used
# notice that with echo = TRUE 
source(file = "/Users/zarawaheed/Documents/BostonUniversity/MA615/Homework/HW_1/hand_functions.R", echo = TRUE)

# Now use the function from hand_functions.R

sp_out <- sum_special(mtcars_mpg2)
```

```{r setup, include=FALSE}
# library(esquisse)
# 
# esquisser(data = mtcars_mpg2, viewer = "browser")


ggplot(mtcars_mpg2) +
  aes(x = disp, y = mpg) +
  geom_point(shape = "bullet", size = 4L, colour = "#B22222") +
  geom_smooth(span = 0.5) +
  theme_minimal()

```

```{r setup, include=FALSE}
# note that this boxplot cannot be made with esquisse() unless
# the data is adjusted.  What adjustment is needed?
#'arg' must be NULL or a character vector
ggplot(mtcars_mpg2, aes(x=as.factor(cyl), y=mpg)) + 
  geom_boxplot(fill="slateblue", alpha=0.2) + 
  xlab("cyl")
```
